A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-02-23 sections/Overview.tex
Example for S2.5

>>>>

Take the following worklist as an example
$$\al \Vdash \blue{(\lam x)~() \To_a a \le \al} , x:\al, \bt \Vdash \blue{\al \le \bt} \Vdash \blue{\bt \le 1}$$
A worklist is structurally a stack with its top element to the right.
There are three (blue-colored) judgment chains in the worklist,
where the first and second judgment chains are two subtyping judgments,
and the third judgment chain, $(\lam x)~() \To_a a \le \al$,
is a sequence of an inference judgment followed by a subtyping judgment.

The algorithm first analyse the two subtyping judgments and
will find the best solutions $\al = \bt = 1$
(please refer to Figure~\ref{fig:alg} for detailed derivations).
Then we substitute every instance of $\al$ and $\bt$ to $1$,
so the variable declarations can be safely removed from the worklist.
Now we reduce the worklist to the following state
$$\nil \Vdash \blue{(\lam x)~() \To_a a \le 1}, x:1$$
which has a term variable declaration as the top element.
Because no judgments before the declaration refer to $x$,
as a basic property of an ordered context
(Figure~\ref{fig:alg:syntax} shows its well-formedness criteria),
we remove all declarations before the first judgment chain to collect unused variables.
As a result all garbage variables are collected
once the judgment chains refering to them are processed.

After that, we proceed the last judgment chain from the left,
namely an inference judgment $(\lam x)~()\To~?$, with the unit type $1$ as its result.
Finally the last judgment becomes $1 \le 1$, and is satisfied as a base case.
